Discovering causal factors with back-to-back regression

### 2019-05-22 paper/meg_exps.tex
meg exps

% Finally,
\paragraph{Back-to-back regression} was fit as described earlier using two
additional stability tricks designed to minimize the impact of bagging.  First
the $G$ ridge regression was broken-down with SVD blablabla Second, $X$ was
regularized using a maximal likelihood blablabla Third, no regularization

Back-to-back regression directly leads to $\hat E$.

>>>>

\paragraph{Back-to-back regression} We adapted back-to-back regression with two
changes. First, to avoid getting a slightly positively-biased estimate of the
factors contributing to the MEG signal, we swap the Tikhonov regularization of
the first regression $G$ with a trunkated regularization. Trunkation was fitted
 by maximum likelihood estimate, as implemented in scikit-learn principal
 component analysis. Second, to minimize the variance increase induced by
 bagging, we computed the inverse regularized covariance matrices outside
 bagging:
\begin{equation}
G = (Y_^T Y+\lambda_Y I)^{-1} Y_i^T X_i
\end{equation}
